---
title: "A linear regression package in R"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{A linear regression package in R}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```



## About the Package
This package has implemented a class based solution for linear regression. It uses a ordinary linear algebra and calculate:

* Regressions coefficients
* The fitted values
* The residuals
* The degrees of freedom
* The residual variance
* The variance of the regression coefficients
* The t-values for each coefficient

### Setup of Package 
```{r setup}
library(lab4)
linreg_mod <- linreg$new(Petal.Length ~ Species, data=iris)
```

### Print function
Function to print the formula and intercept for the linear regression model
```{r}
linreg_mod$print()
```

### resid function 
Function to calculate the resID
```{r}
linreg_mod$resid()
```
### resid function 
Function to calculate the resID
```{r}
linreg_mod$resid()
```
### pred function 
Function to show pred
```{r}
linreg_mod$pred()
```

### coef function 
Function to calculate the coef
```{r}
linreg_mod$coef()
```
### plot function 
Function to show the plot
```{r}
linreg_mod$resid()
```
### summary function 
Function to show the summary
```{r}
linreg_mod$summary()
```
